Parsing Postfix log files

### 2009-03-06 doc/logparser-architecture.tex
Wrote architecture conclusion.

Actions may return a modified input line to the framework that will be
parsed as if read from the input stream, allowing for a simplified version
of cascaded parsing~\cite{cascaded-parsing}.  This powerful facility allows
several rules and actions to parse a single input, potentially simplifying
both rules and actions.  A simple example is to have one rule and action
removing comments from input lines, so that other rules and actions do not
have to handle comments at all; obviously if comment characters can be
escaped or embedded in quoted strings the implementation needs to be more
complex, but for some inputs this can greatly simplify subsequent parsing.

@@

XXX TO BE WRITTEN\@.

>>>>

Actions may return a modified input line to the framework that will be
parsed as if read from the input stream, allowing for a simplified version
of cascaded parsing~\cite{cascaded-parsing}.  This powerful facility allows
several rules and actions to parse a single input, potentially simplifying
both rules and actions.  A simple example is to have one rule and action
removing comments from input lines, so that other rules and actions do not
have to handle comments at all; obviously if comment characters can be
escaped or embedded in quoted strings the implementation needs to be more
complex, but for some inputs this can greatly simplify subsequent parsing.
Actions do not need to be specially registered with the framework or be
declared in a particular way to use cascaded parsing: actions that do not
use cascaded parsing will return nothing, those that do will simply return
a string to be parsed.

@@

This chapter has presented the parser architecture developed for this
project.  It started with a high level view of the architecture, describing
how it achieves its design aim of being easily extensible for users, and
the advantages that being easily extensible brings to parser authors too.
The three main components of the architecture were documented in detail,
explaining each component's responsibilities and the functionality it
provides, plus any difficulties associated with the components.  The
framework, unsurprisingly, was quite quick to document, because it is the
simplest of the three components.  The actions are also quite easy to
understand, because the architecture does not impose any structure or
requirements upon them: parser authors are free to do anything they want
within an action.  The architecture's support for cascaded parsing was
described in the actions section, with an example to illustrate how it can
be useful.  The rules section was the longest, because although the rules
appear conceptually simple --- recognise an input and specify the action
that handles that input --- they have subtle behaviour that needs to be
clearly explained.  When extending a ruleset a decision needs to be taken
about whether the input should be recognised by extending an existing rule,
by adding a new rule to an existing rule category, or by adding a new rule
category, rule, and action.  Rules can have conditions attached to them,
restricting the set of rules used to recognise an input; the complexity of
the conditions used greatly influences the difficulty of writing a correct
ruleset or understanding and extending an existing ruleset.  Overlapping
rules are frequently a requirement in a parser, and their use can greatly
simplify some rules, but they can be a source of bugs because they can
recognise inputs unexpectedly.  The framework does not try to detect
overlapping rules, because overlap amongst rules may be valid and is quite
often intentional; that responsibility falls to the author of the rules.
The difficulty involved in detecting overlap is proportional to the
complexity of a ruleset's regexes and conditions, and may be possible for a
human yet intractable or impossible for a program.  The rules section
finishes with a discussion of pathological rules, concentrating on
pathological regexes.
